Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-27 paper.tex
more edits section 2

The transition relation $\judgeCreduce{s}{s}$ is parameterized over
$applyCast$ to allow for the differences between D and UD.
%
When evaluating a cast expression, the machine moves the cast to the
continuation and evaluates the inner expression.
%% Other
%% transition rules starting from$Eval$states are standard.
To apply a casted function, the machine first casts $v_1$, the operand, then
applies $v_2$ (the underlying function) to the casted operand, and finally cast
the return value.
%
To take out the first (resp. second) part of a casted pair, the
machine firstly takes out the first (resp. second) part of $v$, the
underlying pair, and cast the result.
%
%In case splitting, if the target value is a left injection, the
%machine moves to a state that will apply the first continuation
%function to the value inside the left injection. The case for right
%injection is similar.
%
To case split a casted injection, the machine moves the cast from
the injection to continuations functions.
%
To cast a value, the machine invokes $applyCast$ on the value. If the cast 
succeeds ($\rOOsucc{v'}$), the machine returns the result to the next
continuation.  If the cast fails ($\rOOfail{l}$), the machine halts with the 
blame label.
%Let $r$ range over cast results. A cast result is either a success, which 
%brings back a value, or a failure, which brings back a blame label.

@@

Next, we define the CEK Machine for \lazyUD{}. The only difference with
respect to \lazyD{} is in the definition of the $\mathit{applyCast}$
function, in which a cast whose source or target is the unknown type
$\star$ is always split into two casts that go through an injectable
type, that is, a type in which all sub-components are the unknown
type, such as $\star \to \star$.

>>>>

The transition relation $\judgeCreduce{s}{s}$ is parameterized over
$applyCast$ to allow for the differences between D and UD.
%
When evaluating a cast expression, the machine moves the cast to the
continuation and evaluates the inner expression.
%% Other
%% transition rules starting from$Eval$states are standard.
To apply a casted function, the machine first casts $v_1$ (the operand), then
applies $v_2$ (the underlying function) to the casted operand, and then finally
casts the return value.
%
To take out the first (resp. second) part of a casted pair, the
machine firstly takes out the first (resp. second) part of $v$, the
underlying pair, and cast the result.
%
%In case splitting, if the target value is a left injection, the
%machine moves to a state that will apply the first continuation
%function to the value inside the left injection. The case for right
%injection is similar.
%
To case split a casted injection, the machine moves the cast from
the injection to continuations functions.
%
To cast a value, the machine invokes $applyCast$ on the value. If the cast 
succeeds ($\rOOsucc{v'}$), the machine returns the result to the next
continuation.  If the cast fails ($\rOOfail{l}$), the machine halts with the 
blame label.
%Let $r$ range over cast results. A cast result is either a success, which 
%brings back a value, or a failure, which brings back a blame label.

@@

Next, we define the CEK Machine for \lazyUD{}. The only difference with
respect to \lazyD{} is in the definition of the $\mathit{applyCast}$
function, in which a cast whose source or target is the dynamic type
$\star$ is always split into two casts that go through an injectable
type, that is, a type in which all sub-components are the dynamic
type, such as $\star \to \star$.
